---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ABMR6

<!-- badges: start -->
<!-- badges: end -->

The goal of this repository is to illustrate how to use R6 to perform individual-based simulations using R6 (https://github.com/r-lib/R6).

After cloning this repos (note: this repos is not a package), you can simply follow the steps described in `master.R` to run the simulations. Then explore the other files to see how this works (there are examples defined for each class that can really help!).

Here is a subset of such content:
```{r}
library(R6)
set.seed(123)
example <- FALSE
source("World.R")
source("Butterfly.R")
source("Population.R")
source("Simulation.R")
simu <- Simulation$new(years = 200, N = 500, mutation_rate = 1e-2, period = 50)
simu$run()
simu$plot()
```

The example treated here is inspired in part by the well known peppered moth evolution story (https://en.wikipedia.org/wiki/Peppered_moth_evolution). It considers that the environment is either black or white and that the colour switches regularly. The grey line on the plot shows the colour of the environment (top means black and bottom means white). The blue line shows how the allele frequency for the gene coding the black colour evolves through time. Evolution happens because of both drift and selection. The selection happens because I considered that moths (or butterflies in the files) have a lower fitness if they are not in an environment matching their colour (because, say, the predators spot them better).
